Compiling refinement types to dependent types

### 2020-07-09 tex/paper.tex
Add a note on ADTs having only a single field each
Remove bools
1. Units + ADTs are good enough to build up bools
2. We don't really need not use bools.
Write down what \top means now

\newcommand{\Unit}{\textbf{Unit}}
\newcommand{\Int}{\textbf{Int}}

@@

@@

We also have the following concessions:
\begin{itemize}
  \item The syntax only allows refinements on base types.
    Note that this does not restrict the expressive power of the language.
    For instance, a refinement on a function that we might otherwise wish to write as
    \[
      (x : \Int) \rightarrow \{ v : \Int \rightarrow \Int | v x = 0 \} \rightarrow \Int
    \]
    might instead be expressed via a dummy parameter:
    \[
      (x : \Int) \rightarrow (f : \Int \rightarrow \Int) \rightarrow \{ \_ : \Unit | f x = 0 \} \rightarrow \Int.
    \]
\end{itemize}

>>>>

\newcommand{\unit}{u}
\newcommand{\Unit}{\textbf{Unit}}
\newcommand{\Int}{\textbf{Int}}

@@

We introduce a shorthand notation $\top$ denoting a tautologically true \emph{proposition},
used for trivial refinements that do not carry any extra information.
One good way to define $\top$ is the equality of the sole member of $\Unit$ to itself:
$\top \triangleq \unit = \unit$.

@@

We also have the following concessions:
\begin{itemize}
  \item The syntax only allows refinements on base types.
    Note that this does not restrict the expressive power of the language.
    For instance, a refinement on a function that we might otherwise wish to write as
    \[
      (x : \Int) \rightarrow \{ v : \Int \rightarrow \Int | v x = 0 \} \rightarrow \Int
    \]
    might instead be expressed via a dummy parameter:
    \[
      (x : \Int) \rightarrow (f : \Int \rightarrow \Int) \rightarrow \{ \_ : \Unit | f x = 0 \} \rightarrow \Int.
    \]
  \item Our algebraic data types only allow a single ``field'' in each constructor.
    One way to alleviate this is to introduce tuples,
    but doing so would complicate the exposition
    without any benefit for illustrating the main idea of this work.
\end{itemize}
